Can Symmetric Cryptography Be Liberated from the Von Neumann Style?

### 2024-12-11 paper.tex
About equality
Reviewer A:
  Quelque chose que j'ai trouvé un peu trop implicite, en terme de
  description de la formalisation, c'est sur le traitement des
  égalités. Je devine que les algèbres de Bool que vous considérez
  doivent être des algèbres de Bool par rapport à l'égalité native de
  Coq, pas de quotient. C'est un peu limitant, mais ça n'a pas l'air
  de vous poser de problème en pratique. J'aurais probablement aimé un
  peu plus de commentaire là-dessus.

The type \coqe!bool! is an obvious instance of a Boolean algebra.
However, any commutative applicative~\citep{mcbride:applicative}
functor \coqe!F! applied to a Boolean algebra also yields a Boolean
algebra (dispatching the Boolean operations pointwise to the
underlying elements). For the sake of completeness, we recall that an
applicative functor offers the following operations:
%
\coqfrom{Algebra}{Applicative}
%
subject to an equational theory expressing the fact that applicative
functors correspond to lax monoidal
functors~\citep{maclane:working-categorist} over the Cartesian product
type. Commutativity of an applicative functor \coqe!F! states that
arguments can be reduced in any order:
%
\coqfrom{Algebra}{ApplicativeComm}

>>>>

The type \coqe!bool! is an obvious instance of a Boolean algebra.
However, any commutative applicative~\citep{mcbride:applicative}
functor \coqe!F! applied to a Boolean algebra also yields a Boolean
algebra (dispatching the Boolean operations pointwise to the
underlying elements). For the sake of completeness, we recall that an
applicative functor offers the following operations:
%
\coqfrom{Algebra}{Applicative}
%
subject to an equational theory expressing the fact that applicative
functors correspond to lax monoidal
functors~\citep{maclane:working-categorist} over the Cartesian product
type. Commutativity of an applicative functor \coqe!F!
states\footnote{For conceptual simplicity, we shall state our
properties using an extensional equality throughout this article: two
functions can be substituted for one another ---they are equal--- if
they produce the same outputs given the same inputs. Given our focus
on terminating functions (cryptographic primitives) from finite types
to finite types (blocks of plaintext to blocks ciphertext), this is
perfectly justified, even in an intuitionist type-theory such as the
Calculus of Inductive Constructions of Coq.} that arguments can be
reduced in any order:
%
\coqfrom{Algebra}{ApplicativeComm}
